PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-09-11 qfenv_paper/qf_environment.tex
Completed draft!

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{5}, 
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from the PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent or star-forming based on an evolving specific star formation cut, and as low or high density environments based on fixed cylindrical aperture environment measurements on a volume-limited Environment Definition Population (from PRIMUS and SDSS). For quiescent and star-forming galaxies in low or high density environments, we examine the evolution of their stellar mass function (SMF) evolution. Then using the SMFs we compute the $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify the evolution of $f_{\rm{Q}}(\mathcal{M}_{*})$ within our redshift range. We find that in both low and high density environments the quiescent fraction increases with cosmic time. Moreover, we illustrate that galaxy populations in high density environments have significantly higher quiescent fractions than galaxy populations in low density environments. Furthermore, by comparing the quiescent fraction evolutions, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments. These results suggest that quenching due to the environment has a moderate effect on the quiescent fraction evolution and provide constraints on quenching mechanisms in high density environments such as groups and clusters. 
\end{abstract}

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) from SDSS. These $f_{\rm{red}}$ values are calculated from the best-fit parameterizations presented in the respective works. High density environment is represented in red and low density environment is represented in blue. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure}

@@

In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross). From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$). For \cite{geha12a}, we plot $f_{\rm{Q}}$ in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} \sim 10^{10.55} \mathcal{M}_{\odot}$.
%Add sentence about how the varying environment classification helps with the comparison.

For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with other SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment. For example, \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurements make direct comparisons unclear, in their corresponding higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, which is in agreement with our high density environment. Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.

@@

A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to obtain $f_{\rm{Q}}$ for isolated galaxies over a wider mass range ($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2} \mathcal{M}_{\odot}$). Provided that \cite{geha12a} probe a slightly lower redshift range ($ z \le 0.06$), \cite{geha12a} present a consistent $f_{\rm{Q}}$ range as our SDSS $f_{\rm{Q}}$. Within the overlapping mass range, at the low mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot}) \sim 0.8$. Both of these values agree with our lowest redshift $f_{\rm{Q}}$ results.

@@

In Section \ref{sec:qffit}, we pointed out that $f_{\rm{Q}}$ in low density environment evolved over cosmic time. From this trend we deduce that internal, environment independent, quenching mechanisms contribute to star-formation quenching in galaxy evolution. \cite{Iovino:2010aa} from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}, also find that $f_{\rm{Q}}$ in low density environment increases over decrease in redshift. On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\rm{Q}}$ in low density environment decreases over cosmic time. This disagreement persists even when we account for the galaxy classification discrepancies in Figure \ref{fig:qffit_comp}.

Furthermore, in Section \ref{sec:qffit}, our comparison of the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment revealed a modicum of evidence for the existence of environment dependent quenching mechanisms. The same comparison on zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present trends inconsistent with our findings. First, comparing the high (red) and low (blue) density environments for \cite{Iovino:2010aa} in Figure \ref{fig:qffit_comp} shows that there is indeed pronounced discrepancies between the $f_{\rm{Q}}$ evolution in different environments. Group galaxies in \cite{Iovino:2010aa} have higher overall $f_{\rm{Q}}$ than isolated galaxies. However, unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds the opposite environment dependence that there is a significantly greater $f_{\rm{Q}}$ evolution for isolated galaxies.

@@

While the zCOSMOS survey provides more precise spectroscopic redshift than PRIMUS, our sample provides a significantly larger statistics. As listed in Table \ref{tab:subsample}, even after our edge effect cuts and stellar mass completeness limits, our sample consists of $12,861$ galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from SDSS over $0.05 < z < 0.12$. Meanwhile, \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ over $0.1 < z < 0.8$. But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. In comparison, our PRIMUS sample alone contains $> 20$ times the number of galaxies. Given the difference in sample size, much of the evolutionary trend discrepancy between the \cite{Iovino:2010aa} results and our results could be attributed to the limited statics in \cite{Iovino:2010aa}.

The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$). Although the sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, it contains sufficient statistics for a more s

In addition to the number of galaxies, our sample covers a larger portion of the sky. Our SDSS-{\em GALEX} sample covers $2,505 \rm{deg}^2$. More comparably, our PRIMUS sample covers $5.5 \rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS, $1.7 \rm{deg}^2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

While the zCOSMOS survey provides more precise spectroscopic redshift than our sample derived from PRIMUS, our sample provides significantly larger statistics. As listed in Table \ref{tab:subsample}, our sample consists of $64,026$ galaxies from SDSS and $12,861$ galaxies from PRIMUS totaling $76887$ galaxies. Meanwhile \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ and $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ and $0.1 < z < 0.8$. But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. The more recent \cite{Kovac:2014aa} provides larger statistics with $2340$ galaxies with $0.1 < z < 0.4$ and $2448$ galaxies with $0.4 < z < 0.7$; however falls short of our PRIMUS sample. Furthermore, our sample derived from SDSS-{\em GALEX} and PRIMUS cover $2505 \rm{deg}^2$ and $5.5 \rm{deg}^2$ respectively. Compared to zCOSMOS, which covers $1.7 \rm{deg}^2$ of the sky, our sample provides significantly greater sky coverage and thus less affected by cosmic variance. 
% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1

Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe. Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\citealt{Baldry:2006aa, Peng:2010aa}). From the mass-dependence presented in all $f_{\rm{Q}}$ in Figure \ref{fig:qf}, we concur that galaxy stellar mass plays a significant role in quenching. Furthermore, since $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching. %However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease. This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$. We find that this is not the case. % What does this have to say about physical processes in groups and clusters that affect quenching?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Discussion} \label{sec:summary}
Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $z < 0.8$. From these stellar mass functions, we compare the proportion of quiescent galaxies within the subsamples by computing quiescent fraction for each of them. Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass. From our analyses we find the following notable results.

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
Alison~Coil\altaffilmark{2}, 
Richard~Cool\altaffilmark{3}, 
Daniel Eisenstein\altaffilmark{4},
John Moustakas\altaffilmark{5}, 
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from the PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent or star-forming based on an evolving specific star formation cut, and as low or high density environments based on fixed cylindrical aperture environment measurements on a volume-limited Environment Definition Population (from PRIMUS and SDSS). For quiescent and star-forming galaxies in low or high density environments, we examine the evolution of their stellar mass function (SMF) evolution. Then using the SMFs we compute the $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify the evolution of $f_{\rm{Q}}(\mathcal{M}_{*})$ within our redshift range. We find that in both low and high density environments the quiescent fraction increases with cosmic time. Moreover, we illustrate that galaxy populations in high density environments have significantly higher quiescent fractions than galaxy populations in low density environments. Furthermore, by comparing the quiescent fraction evolutions in the environments, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments. These results suggest that environment dependent quenching has a moderate effect on the quiescent fraction evolution. Furthermore our results provide constraints on the effect of environment on star-formation quenching.
\end{abstract}

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS. The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, and \cite{Baldry:2006aa} are calculated from the best-fit parameterizations presented in the respective works. The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. High density environment is represented in red and low density environment is represented in blue. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure}

@@

In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross). From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$). For \cite{geha12a}, we plot $f_{\rm{Q}}$ in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.

For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with other SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment. For example, \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurements make direct comparisons unclear, in their corresponding higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, which is in agreement with our high density environment. Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$. The \cite{Baldry:2006aa} points (diamond) in Figure \ref{fig:qffit_comp} reflect this agreement.

@@

A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to obtain $f_{\rm{Q}}$ for isolated galaxies over a wider mass range ($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2} \mathcal{M}_{\odot}$). Provided that \cite{geha12a} probe a slightly lower redshift range ($ z \le 0.06$), \cite{geha12a} present a consistent $f_{\rm{Q}}$ range as our SDSS $f_{\rm{Q}}$. Within the overlapping mass range, at the low mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot}) \sim 0.8$. Both of these values agree with our lowest redshift $f_{\rm{Q}}$ results in low density environment. Figure \ref{fig:qffit_comp} illustrates the $f_{\rm{Q}}$ agreement for $\mathcal{M}_{*} = 10^{10.5} \mathcal{M}_{\odot}$.

@@

In Section \ref{sec:env_qf_evol}, we pointed out that $f_{\rm{Q}}$ in low density environment evolved over cosmic time. From this trend we deduce that internal, environment independent, quenching mechanisms contribute to star-formation quenching in galaxy evolution. \cite{Iovino:2010aa} from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}, also find that $f_{\rm{Q}}$ in low density environment increases over decrease in redshift. On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\rm{Q}}$ in low density environment decreases over cosmic time. This disagreement persists even when we account for the galaxy classification discrepancies in Figure \ref{fig:qffit_comp}.

Furthermore, in Section \ref{sec:env_qf_evol}, our comparison of the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment revealed a modicum of evidence for the existence of environment dependent quenching mechanisms. The same comparison on zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present trends inconsistent with our findings. First, comparing the high (red) and low (blue) density environments for \cite{Iovino:2010aa} in Figure \ref{fig:qffit_comp} shows that there is indeed pronounced discrepancies between the $f_{\rm{Q}}$ evolution in different environments. Group galaxies in \cite{Iovino:2010aa} have higher overall $f_{\rm{Q}}$ than isolated galaxies. However, unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds the opposite environment dependence that there is a significantly greater $f_{\rm{Q}}$ evolution for isolated galaxies.

@@

While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides a significantly larger statistics. In addition, our sample covers a larger portion of the sky. Our SDSS-{\em GALEX} sample covers $2,505 \;\rm{deg}^2$. More comparably, our PRIMUS sample covers $5.5 \;\rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS, $1.7 \;\rm{deg}^2$. With a significantly greater sky coverage our sample is less susceptible to cosmic variance.

As listed in Table \ref{tab:subsample}, after our edge effect cuts and stellar mass completeness limits, our sample consists of $12,861$ galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from SDSS over $0.05 < z < 0.12$. Meanwhile, \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ over $0.1 < z < 0.8$. But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. In comparison, our PRIMUS sample alone contains $> 20$ times the number of galaxies. While there is a considerable difference in the overall $f_{\rm{Q}}$ between our results and those of \cite{Iovino:2010aa}, the use of different methodologies, particularly for galaxy classification and environment measurements, make the comparisons ambiguous. On the other hand, the discrepancies in the $f_{\rm{Q}}$ evolutionary trends with our results may be explained by the limited statistics in the \cite{Iovino:2010aa} sample.

The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$). Although their sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, the \cite{Kovac:2010aa} sample provides a more stable comparison.  Once their results are adjusted for the different galaxy classification, we find that their overall $f_{\rm{Q}}$ is more or less consistent with our overall $f_{\rm{Q}}$. However, it is difficult to explain the significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Discussion} \label{sec:summary}
Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $0.05 < z < 0.8$. From these stellar mass functions, we compare the proportion of galaxies that have quenched their star-formation within the subsamples by computing quiescent fraction for each of them. Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass. From our analyses we find the following notable results.

\begin{enumerate}
	\item By measuring the SMF evolution for each of our subsamples, we approximately trace the evolutionary tracks our galaxy population tracing the tracks of quenching mechanisms and galaxies infalling into high density environments. 
	\item From the SMFs, we find that our galaxy population in high density environments, both star-forming and quiescent, have a higher median mass, thus confirming the mass density relation and mass-segregation in different environments throughout our sample's redshift range. 
	\item For all subsamples, $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass showing a clear mass dependence and supporting well established color-mass and morphology mass relations. 
	\item $f_{\rm{Q}}$ increases significantly with redshift for both low and high density environments. For high density environment, this trend is the Butcher-Oemler effect. Furthermore, the $f_{\rm{Q}}$ evolution in low density environment suggest the existence of internal environment-independent quenching mechanisms. 
	\item By fitting our $f_{\rm{Q}}$s, we illustrate that $f_{\rm{Q}}$ in high density environments is greater than $f_{\rm{Q}}$ in low density environments regardless of mass and redshift. This result reflects the well known trend that galaxies in high density environment are statistically redder, have lower SFRs, and more massive. 
	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for a range of environment classifications reveal that the since $z = 0.8$, $f_{\rm{Q}}$ has evolved by a greater amount in higher density environments. For our purest high environment sample ($n_{\rm{env}} > 9$), the total $f_{\rm{Q}}$ evolution is $\sim 0.1$ greater than the total $f_{\rm{Q}}$ evolution in low density environment, revealing a moderate dependence in environment. 
\end{enumerate}

Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe. Recently star-formation quenching has often been classified into internal or external mechanisms, and sometimes more specifically into mass-dependent and environment-dependent mechanisms (\citealt{Baldry:2006aa, Peng:2010aa}). The significant redshift evolution of the $f_{\rm{Q}}$ in low density environment confirms the existence of internal mechanisms that quench star-forming in galaxies.

Furthermore, the greater $f_{\rm{Q}}$ evolution in high density environment over low density environment demonstrates that in addition to the internal quenching mechanisms, in high density environments such as groups and clusters, environment-quenching also contributes to star-formation quenching. Although our results do not specifically shed light on which quenching mechanism (e.g. strangulation, ram-pressure stripping, etc.) occur in high density environments, they impose strict constraints on the total contribution of environment quenching that any environment quenching model must satisfy. More importantly, our results provide limit on the role of environment quenching in galaxy evolution.

\bigskip 
We thank people ...

Support for this work was provided by ...

something something, details details

The SDSS is managed by the Astrophysical Research Con- sortium for the Participating Institutions. The Participating In- stitutions are the American Museum of Natural History, As- trophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Ad- vanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck- Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
%
% References
%
\bibliography{PRIMUS}
\end{document}
